Regression Discontinuity Design to Measure Incumbency Advantage in US Congressional Elections

### 2023-04-25 sandbox/STAT530_ProjectSlides.qmd
Add files via upload

**Introduction**: regression discontinuity design (RDD) is a quasi-experimental pretest-posttest design that aims to determine the causal effects of interventions by assigning a cutoff or threshold above or below which an intervention is assigned.

@@

**Goal**: Try to estimate the causal effect of intervention/treatment, $\tau(W=w_0)$, at $W=w_0$ on $Y$ with covariate $X$.

@@

We can test for validity of the continuity assumption using our observed data:

@@

@@

| Data Set 1           | Data Set 2   |
| -------------------- | ------------ |
| Year                 | Year         |
| State                | State        |
| District             | District     |
| **Dem. Vote Margin** | Unemployment | 
| Candidate            | Race         |
|                      | Education    |

@@

@@

>>>>

**Introduction**: Regression discontinuity design (RDD) is a quasi-experimental pretest-posttest design that aims to determine the causal effects of interventions by assigning a cutoff or threshold above or below which an intervention is assigned.

@@

**Goal**: Try to estimate the causal effect of intervention/treatment, $\tau(W=w_0)$, at $W=w_0$ on $Y$ with (unobserved/observed) covariate $X$, where individual assignment is determined by value of $W_i$ through $D_i=1\{W_i\ge w_0\}$.

@@

We empirically can test for validity of the continuity assumption using our observed data:

@@

We use the Imbens-Kalyanaraman optimal bandwidth formula to calculate the optimal bandwidths used in our local regression estimation.

@@

| Data Set 1           | Data Set 2    |
| -------------------- | ------------- |
| Year                 | Year          |
| State                | State         |
| District             | District      |
| **Dem.* Vote Margin** | Unemployment | 
| Candidate            | Race          |
|                      | Education     |

@@

*Dem. = Democrat (Party)

@@

## Sources:

  1. Lee, David S.; Randomized experiments from non-random selection in U.S. House elections, Journal of Econometrics 142 (2008) 675–697
  2. de la Cuesta, Brandon and Imai, Kosuke; Misunderstandings About the Regression Discontinuity Design in the Study of Close Elections, Annu. Rev. Polit. Sci. 2016. 19:375–96
  3. Calonico et al.; Regression Discontinuity Designs Using Covariates; The Review of Economics and Statistics, 2019, 101(3): 442–451
  4. McCrary, Justin; Manipulation of the running variable in the regression discontinuity design: A density test; Journal of Econometrics 142 (2008) 698–714

## Audience Discussion and Questions
